\chapter{GNSS\_composite}\label{cha:gnss}

This class generates the autocorrelation function of a set of GNSS signals.\\

Example of object construction with arbitrary name {\it my\_GNSS\_func}:\\

\texttt{my\_GNSS\_func = wavpy.GNSS\_composite()}\\

In this case, public variables and functions from object {\it my\_GNSS\_func} of class {\it GNSS\_composite} can be respectively checked/modified or called with:\\

\texttt{my\_GNSS\_func.variable}\\

\texttt{my\_GNSS\_func.function()}\\


\section{Public variables}

\begin{itemize}
\item {\bf lambda\_size} (integer): Number of samples of the autocorrelation function. Default value: 157

\item {\bf weight\_CA} (float): Weight for the C/A code (GPS L1). Default value: 1.0

\item {\bf weight\_PY} (float): Weight for the PY code (GPS L1). Default value: 1.0

\item {\bf weight\_M} (float): Weight for the M code (GPS L1). Default value: 1.0

\item {\bf weight\_IM} (float): Weight for the Inter-Modulation component (GPS L1). Default value: 1.0

\item {\bf weight\_E1A} (float): Weight for the A code (Galileo E1). Default value: 0.0

\item {\bf weight\_E1B} (float): Weight for the B code (Galileo E1). Default value: 0.0

\item {\bf weight\_E1C} (float): Weight for the C code (Galileo E1). Default value: 0.0

\item {\bf weight\_B1I} (float): Weight for the C code (BeiDou B1). Default value: 0.0

\item {\bf weight\_L1C} (float): Weight for the L1C code (QZSS). Default value: 0.0

\item {\bf frequency} (double): Frequency of the GNSS signal. Default value: 1575420000.0 (GPS L1)
\end{itemize}

\section{Relevant private variables}

\begin{itemize}
\item {\bf lambda\_func} (double, array of {\bf lambda\_size} elements): Normalized autocorrelation function stored. Default value: GPS-L1 autocorrelation function with all code components.

\item {\bf sampling\_rate} (double): Sampling rate of the receiver in samples/sec. Default value: 80000000.0

\item {\bf filter\_BB\_BW} (double): Base-band bandwidth of the filter applied in Hz. Default value: 12000000.0
\end{itemize}

\section{Functions}

\subsection{dump\_parameters}

Print relevant information about the object's content (public and private variables).\\

Example:\\

\texttt{my\_GNSS\_func.dump\_parameters()}\\


\subsection{set\_instrumental\_params}

Set the instrumental parameters that have to be taken into account for the computation of the autocorrelation function.\\

Example:\\

\texttt{my\_GNSS\_func.set\_instrumental\_params(sampling\_rate, filter\_BW, computeLambda)}\\

Input variables:
\begin{itemize}
\item {\bf sampling\_rate} (double): Input sampling rate in samples/sec.
\item {\bf filter\_BW} (double): Input base-band bandwidth of the filter applied in Hz.
\item {\bf computeLambda} (char): "1" if you want to compute the autocorrelation function with this function call, or "0" if you just want to set the input parameters without computing the autocorrelation function.
\end{itemize}


\subsection{compute\_lambda\_func}

Compute and store the autocorrelation function according to current configuration.\\

Example:\\

\texttt{my\_GNSS\_func.compute\_lambda\_func()}\\


\subsection{get\_lambda\_func}

Provide the range and values of the autocorrelation function internally stored.\\

Example:\\

\texttt{[range\_lambda, lambda\_func] = my\_GNSS\_func.get\_lambda\_func(range\_len, lambda\_len)}\\

Input variables:
\begin{itemize}
\item {\bf range\_len} (integer): Number of samples of the range of the autocorrelation function (it has to be equal to {\bf lambda\_size}).
\item {\bf lambda\_len} (integer): Number of samples of the autocorrelation function (it has to be equal to {\bf lambda\_size}). 
\end{itemize}

Output variables:
\begin{itemize}
\item {\bf range\_lambda} (double, array of size {\bf range\_len}): Range of the autocorrelation function in meters.
\item {\bf lambda\_func} (double, array of size {\bf lambda\_len}): Normalized autocorrelation function.
\end{itemize}


\subsection{set\_lambda\_func}

Set a given autocorrelation function.\\

Example:\\

\texttt{my\_GNSS\_func.set\_lambda\_func(lambda\_func)}\\

Input variables:
\begin{itemize}
\item {\bf lambda\_func} (double, array of N elements): Normalized autocorrelation function.
\end{itemize}

