\chapter*{References}
\addcontentsline{toc}{chapter}{References}


{\bf [Beyerle, 09]}: Beyerle, G., Carrier phase wind-up in GPS reflectometry, {\it GPS Solutions}, 13, 3, 191-198, doi: 10.1007/s10291-008-0112-1.\\

{\bf [Brown, 78]}: Brown, G.S., Backscattering from a Gaussian-Distributed Perfectly Conducting Rough Surface, {\it IEEE Trans. Antennas and Propagation}, AP-26, No.3, May 1978.\\

{\bf [Cardellach et al, 12]}: Cardellach, E., F. Fabra, A. Rius, S. Pettinato and S. D'Addio, Characterization of Dry snow Substructure using GNSS Reflected Signals, {\it Remote Sensing Environment}, 124, 2012.\\

{\bf [Elfouhaily et al, 97]}: Elfouhaily, T., B. Chapron, K. Katsaros and D. Vandemark, A unified directional spectrum for long and short wind-driven waves, {\it J. Geosphys. Res.}, 102, 15781-15796, 1997.\\

{\bf [Katzberg et al, 06]}: Katzberg, S.J., O. Torres, and G. Ganoe (2006), Calibration of reflected GPS for tropical storm wind speed retrievals, {\it Geophys. Res. Lett.}, vol.33, N.L18602, doi:10.1029/2006GL026825.\\

{\bf [Li et al, 17]}: Li, W., A. Rius, F. Fabra, E. Cardellach, S. Ribó and M. Martín-Neira, Revisiting the GNSS-R Waveform Statistics and its Impact on Altimetric Retrievals, submitted to {\it IEEE Trans. Geosc. Remote Sensing}, 2017.\\

{\bf [Rius et al, 10]}: Rius, A., E. Cardellach and M. Martín-Neira, Altimetric Analysis of the Sea-Surface GPS-Reflected
Signals, {\it Geoscience and Remote Sensing, IEEE Transactions on}, vol. 48, no. 4, pp. 2119-2127, Apr 2010.\\

{\bf [Ulaby et al, 90]}: F. T. Ulaby, R. K. Moore, and A. K. Fung. Microwave Remote Sensing Active and Passive, volume III. Artech House, Inc., 1990.\\

{\bf [Zavorotny and Voronovich, 00]}: Zavorotny, V.U., and A.G. Voronovich, Scattering of GPS signals from the ocean with wind remote sensing application, {\it IEEE Trans. Geosci. Remote Sens.}, 38, 951964, 2000.\\